### 2018-07-12 paper/2-background.tex
Comply with requirements for section heading capitalisation

\subsection{The venerable \Make: static dependencies and file modification times}
\label{sec-background-make}

@@

\subsection{\Excel: dynamic dependencies at the cost of minimality}
\label{sec-background-excel}

@@

\subsection{\Shake: dynamic dependencies with no remorse}
\label{sec-background-shake}

@@

\vspace{-0.5mm}
\subsection{\Bazel: a cloud build system}\label{sec-background-bazel}
\vspace{-0.5mm}

>>>>

\subsection{The Venerable \Make: Static Dependencies and File Modification Times}
\label{sec-background-make}

@@

\subsection{\Excel: Dynamic Dependencies at the Cost of Minimality}
\label{sec-background-excel}

@@

\subsection{\Shake: Dynamic Dependencies with No Remorse}
\label{sec-background-shake}

@@

\vspace{-0.5mm}
\subsection{\Bazel: A Cloud Build System}\label{sec-background-bazel}
\vspace{-0.5mm}

### 2018-07-12 paper/4-build.tex
Comply with requirements for section heading capitalisation

\subsection{The scheduler: respecting the dependency order}
\label{sec-dependency-orderings}

@@

\subsection{The rebuilder: determining out-of-date keys} \label{sec-out-of-date}

@@

Current build systems using deep constructive traces always record hashes of
terminal \emph{input keys}, but the technique works equally well if we skip any
number of dependency levels (say $n$ levels). The input-only approach is the
special case of $n = \infty$, and constructive traces are the special case of
$n = 1$. When $n \ge 2$, deep constructive traces require the tasks to be
\emph{deterministic}, as otherwise it is possible to violate correctness, as
illustrated by an example in~\S\ref{sec-cloud-aspects}.

@@

\subsection{Smarter \hs{[Trace]} data structures}\label{sec-smart-traces}

>>>>

\subsection{The Scheduler: Respecting the Dependency Order}
\label{sec-dependency-orderings}

@@

\subsection{The Rebuilder: Determining Out-of-date Keys}\label{sec-out-of-date}

@@

Current build systems using deep constructive traces always record hashes of
terminal \emph{input keys}, but the technique works equally well if we skip any
number of dependency levels (say $n$ levels). The input-only approach is the
special case of $n = \infty$, and constructive traces are the special case of
$n = 1$. When $n \ge 2$, deep constructive traces require the tasks to be
\emph{deterministic}, as otherwise it is possible to violate correctness, as
illustrated by an example in~\S\ref{sec-cloud-aspects}
(see Fig.~\ref{fig-frankenbuild}).

@@

\subsection{Efficient Data Structures for Traces}\label{sec-smart-traces}
